Speed and Precision in Range Analysis

### 2012-07-05 doc/Manuscript/CLSC/paper.tex
Added CLSC journal paper.

% TODO: discuss more related works: sparsity, and actual implementations.
% TODO: Explain why we are using Stanford
\documentclass[times]{speauth}

% Packages that I must import to compile this latex file:
\usepackage{amssymb}    % To use \mathbb
\usepackage{amsmath}    % To use the equation environment
\usepackage{graphicx}   % For includegraphics
\usepackage{mathpartir} % To use \inferrule
\usepackage{moreverb}   % Requirement from SPE. See if you can remove it.

\usepackage[dvips,colorlinks,bookmarksopen,bookmarksnumbered,citecolor=red,urlco
lor=red]{hyperref}      % Anther requirement from SPE.

@@

@@

\runningheads{V. H. S. Campos {\em et al.}}{Speed and Precision in Range Analysis}

@@

\author{Victor Hugo Sperle Campos, Douglas do Couto Teixeira \\
Igor Rafael Assis Costa, Raphael Ernani Rodrigues and\\
Fernando Magno Quint\~{a}o Pereira\corrauth}

@@

\corraddr{fernando@dcc.ufmg.br}

@@

\maketitle

@@

\bibliographystyle{wileyj}
\bibliography{../references}

>>>>

% TODO: discuss more related works: sparsity, and actual implementations.
% TODO: Explain why we are using Stanford
\documentclass[preprint]{elsarticle}

% Packages that I must import to compile this latex file:
\usepackage{amssymb}    % To use \mathbb
\usepackage{amsmath}    % To use the equation environment
\usepackage{graphicx}   % For includegraphics
\usepackage{mathpartir} % To use \inferrule

@@

\journal{Computer Languages, Systems and Structures}

@@

\begin{frontmatter}

@@

\author{Victor Hugo Sperle Campos, Douglas do Couto Teixeira \\
Igor Rafael Assis Costa, Raphael Ernani Rodrigues and\\
Fernando Magno Quint\~{a}o Pereira%\corrauth
}

@@

@@

\begin{keyword}
kw1 \sep kw2 \sep kw3
\end{keyword}

\end{frontmatter}

@@

\bibliographystyle{model3-num-names}
\bibliography{../references}
